---
title: "PSTAT174_Lab05"
author: "Celeste Herrera"
date: "4/30/2021"
output: pdf_document
---
### **1. We will analyze monthly milk production measured in pounds per from Jan. 1962 to Dec. 1975 from the package tsdl as Lab 4 (if you want to re-install tsdl, please refer to Lab 4). Let’s denote the time series milk as $X_{t}$.**
```{r}
getwd()
setwd("/Users/celesteherrera/Documents/PSTAT174/Lab/Lab05")
```

```{r}
library(tsdl)
milk <- subset(tsdl, 12, "Agriculture")[[3]] 
plot(milk)
```
**(a) Explain why the series milk looks not stationary.**
```{r}
dmilk <- diff(milk,12)
ddmilk <- diff(dmilk,1)
plot(ddmilk)
```

The milk series does not look stationary because the consistency looks a little off.


**(b) Let $Y_{t}$ be the series ddmilk, that is, $Y_{t}$ = (1 - B)(1 - $B^{12}$)$X_{t}$. Plot the ACF and PACF of $Y_{t}$ with lag.max = 50.**
```{r}
acf(ddmilk, lag.max = 50, main = "ACF: First and Seasonally Differenced Time Series")

pacf(ddmilk, lag.max = 50, main = "PACF: First and Seasonally Differenced Time Series")
```


**(c) Now, we assume that $Y_{t}$ corresponds to a SARIMA model. Determine possible candidate models SARIMA(p, d, q) × (P, D, Q)s for the series $Y_{t}$.**
```{r}
library(astsa)
fit <- sarima(xdata = milk,
              p = 0, d = 1, q = 0,
              P = 2, D = 1, Q = 1, S = 12,
              details = F)
fit$fit$coef
```

**(d) Choose one model for this data set, and write down your fitted model.**
```{r}
library(astsa)

fit_1 <- sarima(xdata = milk, details = F,
                p = 0, d =1, q = 0, P = 1, D = 1, Q = 1, S =12)

cat('Coefficents'); fit_1$fit$coef
```

There the equation would be written as $(1- 0.0188B^{12})(1-B)(1-B^{12})X_{t} = (1- 0.6862B^{12})Z_{t}$